\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
more text

In general, we find that the iterative scheme converges within about 50 
iterations, taking about fifteen minutes on a laptop computer. However, since it 
is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, requiring that it be drawn from a distribution whose mean
is a decaying power law in the spherical harmonic degree $l$ in order
to suppress ringing and spurious high order features.
Our full negative log likelihood function in this step is therefore
%
\begin{align}
    \label{eq:nll}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where $\mathbf{f}$ is the measured flux across all targets,
$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
$\mathbf{w}$ are the systematics model weights for all targets,
$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
vectors containing the values of the albedo that are below zero and above one, 
respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
used to smooth the edges of the top-hat prior on $\mathbf{a}$,
$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
%
For simplicity, all our prior covariances are diagonal and
homoscedastic with variances equal to $10^{-2}$ for $\mathbf{w}$, and
$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.

@@

As expected, we obtain a much better fit
The top panel of Figure~\ref{fig:model} shows the median of the maximum likelihood model
across all 95 targets (blue) overplotted on the median flux across
the same targets (black). The median residuals are shown in the bottom panel; these have
standard deviation of less than one percent. While there is significant correlated
structure in the residuals, their power spectrum displays a broad peak extending 
between about 0.1 and 10 days, with a significant dip at 1.00 day. This
suggests our model is fitting the rotational variability of Sol d quite well, but
additional temporal variations---most likely due to cloud movement---cause aperiodic
changes to the reflectivity of the surface. We revisit this point in \S\ref{sec:discussion}.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
    \caption{\label{fig:map_temporal}
             Something.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
    \caption{\label{fig:map_labels}
             Map of Sol d with the major features indicated with suggested
             names.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

>>>>

In general, we find that the iterative scheme converges within about 50 
iterations, taking about fifteen minutes on a laptop computer. However, since it 
is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, requiring that it be drawn from a distribution whose mean
is a decaying power law in the spherical harmonic degree $l$ in order
to suppress ringing and spurious high order features.
Our full negative log likelihood function in this step is therefore
%
\begin{align}
    \label{eq:nll}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where $\mathbf{f}$ is the measured flux across all targets,
$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
$\mathbf{w}$ are the systematics model weights for all targets,
$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
vectors containing the values of the albedo that are below zero and above one, 
respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
used to smooth the edges of the top-hat prior on $\mathbf{a}$,
$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
%
For simplicity, all our prior covariances are diagonal and
homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$, and
$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.

@@

As expected, the second, non-linear step in our optimization procedure
yields a much better fit to the data.
The top panel of Figure~\ref{fig:model} shows the median of the 
maximum likelihood model in this second step
across all 95 targets (blue) overplotted on the median flux (black). 
The median residuals are shown in the bottom panel; these have
standard deviation of less than one percent. While there is significant correlated
structure in the residuals, their power spectrum displays a broad peak extending 
between about 0.1 and 10 days, with a significant dip at 1.00 day. This
suggests our model is fitting the rotational variability of Sol d quite well, but
additional temporal variations---most likely due to cloud movement---cause aperiodic
changes to the reflectivity of the surface. We revisit this point in \S\ref{sec:discussion}.

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
    \caption{\label{fig:map_temporal}
             The inferred mean map when allowing for slight temporal
             variations in the spherical harmonic coefficients. Compare
             to Figure~\ref{fig:map}. An animated version of this figure
             is available on 
             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{GitHub}.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

% \begin{figure}[t!]
%     \begin{centering}
%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
%     \caption{\label{fig:map_labels}
%             Map of Sol d with the major features indicated with suggested
%             names.
%             \codelink{earthshine_S1_S2}
%             }
%     \end{centering}
% \end{figure}
